Automated Verification and Synthesis of Embedded \& Cyber-physical Systems: Advances and Challenges

### 2017-08-02 paper.tex
reviewed section 2.1
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

%--------------------------------------
\subsection{A model for Cyber-physical systems}
\label{ssec:model}
%--------------------------------------

Models are largely employed in science and engineering areas, in order to analyze, predict, and modify the behavior of real-world systems. Specially, deterministic and stochastic models are the basis of many recent engineering advances. The former is uniquely determined by parameter values and previous states, while the latter presents inherent randomness, which is described by probability distributions~\cite{stochmodel}. Nonetheless, one can argue that such models are not enough to represent CPSs, since interaction among different entities (software and hardware components) presents several events that could not be deterministically or stochastically modeled; they can be better represented by nondeterministic approaches~\cite{leeCPS2}. Indeed, that is even more evident when unknown properties are addressed, such as human behavior.

On the one hand, early representations of hybrid systems, {\it i.e.}, systems that mix continuous and discrete dynamics, consisted in instantiating discrete components and discretized continuous dynamics by using discrete models and considering non-modeled effects as uncertainties or perturbations exogenous to them, which can even be negligible. On the other hand, that approach is not suitable for complex CPSs that present intense nondeterminism, where uncertainties play a central role and might invalidate the entire system behavior.

@@

Timed automata employ finite automata with clocks, {\it i.e.}, real variables that follow continuous trajectories with constant slope. Hybrid automata generalize timed automata, also employing finite automata with real variables whose trajectories follow more general dynamical laws~\cite{Henzinger95}.  Timed automata and hybrid automata are deterministic model for hybrid systems that built the basis of HS representations, which were subdivided into different classes of hybrid automata depending on the mapping functions ($r$ and $v$), {\it e.g.}, linear hybrid automata~\cite{Lafferriere99}, rectangular hybrid automata~\cite{Puri94,Henzinger95}, nonlinear hybrid automata~\cite{Henzinger95NL,Broucke1997}, integration graphs~\cite{Kesten1993}, and linear stochastic hybrid automata~\cite{Julius09}.

>>>>

%--------------------------------------
\subsection{A Model for Cyber-physical Systems}
\label{ssec:model}
%--------------------------------------

Models are largely employed in science and engineering areas, in order to analyze, predict, and modify the behavior of real-world systems. Specially, deterministic and stochastic models are the basis of many recent engineering advances. The former is uniquely determined by parameter values and previous states, while the latter presents inherent randomness, which is described by probability distributions~\cite{stochmodel}. Nonetheless, one can argue that such models are not enough to represent CPSs, since interaction among different entities (software and hardware components) presents several events, which could not be deterministically or stochastically modeled; they can be better represented by nondeterministic approaches~\cite{leeCPS2}. Indeed, that is even more evident when unknown properties are addressed, such as human behavior.

On the one hand, early representations of hybrid systems, {\it i.e.}, systems that mix continuous and discrete dynamics, consisted in instantiating discrete components and discretized continuous dynamics by using discrete models and considering non-modeled effects as uncertainties or perturbations exogenous to them, which can even be negligible. On the other hand, that approach is not suitable for complex CPSs, which present intense nondeterminism, where uncertainties play a central role and might invalidate the entire system behavior.

@@

Timed automata employ finite automata with clocks, {\it i.e.}, real variables that follow continuous trajectories with constant slope. Hybrid automata generalize timed automata, also employing finite automata with real variables whose trajectories follow more general dynamical laws~\cite{Henzinger95}.  Timed automata and hybrid automata are deterministic model for hybrid systems that built the basis of HS representations, which were subdivided into different classes of hybrid automata, depending on the mapping functions ($r$ and $v$), {\it e.g.}, linear hybrid automata~\cite{Lafferriere99}, rectangular hybrid automata~\cite{Puri94,Henzinger95}, nonlinear hybrid automata~\cite{Henzinger95NL,Broucke1997}, integration graphs~\cite{Kesten1993}, and linear stochastic hybrid automata~\cite{Julius09}.
